Superphy: Real-time prediction of \textit{E. coli} phenotype using graph-based genome sequence storage and retrieval with the \textit{spfy} module

### 2017-11-10 paper-webserver.tex
EDIT: some cuts / changes here and ther

% 3. how we solved it
In this study, we present an update to the SuperPhy platform, called Spfy. Spfy enables large-scale genome processing in real-time and uniquely decomposses results into graph datastructures for further comparative genomics. Unlike traditional approaches which store results in separate data files or in a relational database, the graph datastructures are then integrated into a knowledge graph identifying relationships between all genomes sequenced in the past, present, and future. We present the use of graph databases as a solution to storing genome analysis results in a meaningful manner, and to allow retrospective comparisons as more genomes are sequenced or populations change.

@@

\section{FUNCTIONALITY}
% ONLY FOCUS ON THE ANALYSIS MODULES
% Describe available functions in spfy
% para covering everything
Spfy performs reference laboratory tasks: O-antigen and H-antigen typing using ectyper \url{https://github.com/phac-nml/ecoli_serotyping}, Shiga-toxin (STX) typing,  virulence factor (VF) and antimicrobial resistance (AMR) gene determination, and related strain determination.

Spfy also performs bioinformatics analyses: pangenome generation, statistical significance testing of genome markers for user-defined groups, and AMR predictions using support vector machines (SVMs).

TODO: List all of the below references in the above paragraphs.
%We introduce one new bioinformatics program, Ecoli-Serotyper (ECTyper) , for determining surface-antigen type and associated VFs, and utilize existing software: the Resistance Gene Identifier (RGI) program \cite{mcarthur2013comprehensive}, Phylotyper \cite{whiteside2017phylotyper}, and Panseq \cite{laing2010pan}.

@@

The entire Spfy update is packaged in Docker \url{https://www.docker.com/} containers and connected together using Docker Compose \url{https://docs.docker.com/compose/}.

@@

TODO: The below was already covered above. No need to repeat. Either here or there, but combine.
%% Task queues are processes which schedule code exection across available computing infrastructure.
%% In Spfy, the Python-based Redis Queue library \url{https://github.com/nvie/rq} is used to manage analysis tasks and run them asynchronously in response to user requests.
%% When a user submits files for analysis or requests population-wide comparisons, separate tasks are enqueued at different priorities, depending on our user experience goals.
%% For example, population-wide analyses have a higher priority than bulk subtyping analyses, as we want search-response queries to return instantly whereas a delay in subtyping is typical in similar web services, such as the Center for Genomic Epidemiology Pipeline (CGE Pipeline) \cite{thomsen2016bacterial}.
%% Spfy enables processing of thousands of genome sequences by using task queue workers running in parallel, which also allows performance to scale to available infrastructure.
%% In addition, the open-source Sentry toolkit \url{https://github.com/getsentry/sentry} was integrated and used for real-time exception tracking and to ensure reliability of the platform.

@@

TODO: bring the docker information from above down here.
The Spfy platform depends on a series of webservers, databases, and task workers and uses \url{https://www.docker.com/}, a virtualization technology, to run self-contained operating systems on the same host computer.
Software packages are installed within the conatiners and the entire platform is networked together using Docker-Compose \url{https://docs.docker.com/compose/}.
(see Figure \ref{fig-docker})
Docker integration ensures that software dependencies, which typically must be manually installed \cite{doi:10.1093/bioinformatics/btu153,laing2010pan,inouye2014srst2,naccache2014cloud}, are handled automatically, and that service runtimes are compartmentalized; this guarantees that code failures do not propagate to other services.

>>>>

% 3. how we solved it
In this study, we present an update to the SuperPhy platform, called Spfy. Spfy enables large-scale genome processing in real-time and uniquely decomposses results into graph data structures for further comparative genomics. Unlike traditional approaches which store results in separate data files or in a relational database, the graph data structures are then integrated into a knowledge graph identifying relationships between all genomes sequenced in the past, present, and future. We present the use of graph databases as a solution to storing genome analysis results in a meaningful manner, and to allow retrospective comparisons as more genomes are sequenced or populations change.

@@

\section{FUNCTIONALITY}
% ONLY FOCUS ON THE ANALYSIS MODULES
% Describe available functions in spfy
% para covering everything
Spfy performs reference laboratory tasks: O-antigen typing, H-antigen typing, and virulence factor (VF) gene determination using ECTyper \url{https://github.com/phac-nml/ecoli_serotyping}, Shiga-toxin (STX) typing using Phylotyper \cite{whiteside2017phylotyper}, and antimicrobial resistance (AMR) gene determination using the Resistance Gene Identifier (RGI) program \cite{mcarthur2013comprehensive}.

Spfy also performs bioinformatics analyses: pangenome generation using Panseq \cite{laing2010pan}, statistical significance testing of genome markers for user-defined groups, and AMR predictions using support vector machines (SVMs).

@@

@@

@@

Docker \url{https://www.docker.com/} is a virtualization technology to run self-contained operating systems on the same host computer.
The Spfy platform depends on a series of webservers, databases, and task workers and uses Docker to compartmentalize these services which are then networked together using Docker-Compose \url{https://docs.docker.com/compose/}.
(see Figure \ref{fig-docker})
Docker integration ensures that software dependencies, which typically must be manually installed \cite{doi:10.1093/bioinformatics/btu153,laing2010pan,inouye2014srst2,naccache2014cloud}, are handled automatically, and that service runtimes are compartmentalized; this guarantees that code failures do not propagate to other services.
